---
title: "About the Team"
---

```{r setup, include=FALSE}
source("utils.R")
```

```{r echo = FALSE}

knitr::opts_chunk$set(collapse = TRUE, comment = "#>")

# Use vertical split by default in this Rmd document
knit_print.htmlwidget <- function(x, ...) {
  # Get the chunk height
  height <- knitr::opts_current$get("height")
  if (length(height) > 0 && height != FALSE)
    x$height <- height
  else
    x$height <- "450px"

  htmlwidgets:::knit_print.htmlwidget(x, ...)
}
```

```{r, echo=FALSE, warning=FALSE}
examples(caption = FALSE, team = TRUE)
```

## Who we are

We're a team of <a href="https://www.ischool.berkeley.edu/" target="_top">Berkeley ISchool</a> graduate students who happen to be passionate about Education, Data Science and the R programming language. This package was initially concepted and built as part of our degree's <a href="https://datascience.berkeley.edu/academics/curriculum/synthetic-capstone-course/" target="_top">Capstone</a> course and featured as a showcase project during December, 2016.

If you'd like to work on helping us extend this package into the future, please create a <a href="https://github.com/gregce/autoCaret/pulls" target="_top">pull request</a> and connect with us!